Anonymous provision of local services via blockchain

### 2022-02-23 access.tex
update anonimity diagram and protocol description

\tfootnote{This paragraph of the first footnote will contain support 
information, including sponsor and financial support acknowledgment. For 
example, ``This work was supported in part by the U.S. Department of 
Commerce under Grant BS123456.''}

@@

\begin{abstract}
Service providers like: lawyers, laboratories, auditors, or banks, to
provide services, require customers to submit data that is often
associated with their personal information. This situation expose
customers to privacy risk. However, most of the service providers use
the personal information merely for logistic operations like payments
and communication, and could provide services anonymously if other means
of logistics would exists.

We propose a framework for coordingating local anonymous service
provision. Our proposal uses blockchain for both anonymous payments and
proofs of existence (so called message board), and content addressable
network (e.g.~IPFS) for results delivery.

The framework can be employed by any local service provider to provide
services without collecting any personal information. Possible
applications for this framework include anonymous clinical drug testing,
steroid testing, parenting testing, anonymous legal advices, or
anonymous financial trustworthiness evaluation.

In case of dispute, either due to exceeding deadlines or providing
incorrect results, the customer can disclose the whole interaction and
prove to the justice (police or court) the misbehaviour of the service
provider.

We analyse the protocol in the context of fairness, and discuss further
extensions to anonymous delivery system, payment with cash, and
decentralized conflict resolution system.

Our framework can potentially enable variety of services that for many
customers base on unacceptable trust assumptions to the SP.
\end{abstract}

\begin{keywords}
Blockchain, anonimity, fair-exchange, physical delivery
\end{keywords}

@@

\maketitle
\section{Introduction}
Service providers (SP) like: lawyers, laboratories, auditors, or banks,
to provide services, require data that is often associated with user
identity.

Providing personal information exposes users to privacy risk,
i.e.~potential loss of control over personal
information~\cite{smith2011information}.

Such user information can be then used deliberately or unintentionally
(e.g, by theft) for: insider disclosure, unauthorized access, or
commercial gains. For example, by reselling it to marketers, financial
institutions, other businesses, government agencies, or even
cybercriminals. Which in turn can lead to profiled advertisements, or
criminal activities like identity theft or illegal tracking and
surveillance~\cite{smith2011information}.

Important individuals like top government, influencers, or celebrities
are especially vulnerable to this kind of attacks as exposure of their
health records, purchase habits, or legal documents can threaten their
reputation, position, or can be used for blackmailing.

The guarantee of the privacy of the data is often based merely on a
trust assumptions and security of IT system. However, most of the SP
don't need the personal information for any other reasons than payment,
or communication, which should be considered secondary compared to
primary matter that is service provision.

It would be desirable if the user could keep its identity private, while
service provider still provide its services. This could lead to reduced
trust that users have to put on SP and less responsibility borne by SP.

@@

Patients willing to take steroid test, drug test, venereal diseases
test, paternity test --- have strong incentive to keep the whole
procedure private. Merely the fact that they took the test --- without
exposing the results --- is suggestive enought to act as a premise in
case of a conflict.

Especially celebrites, politicans and public persona are exposed to this
kind of probems as such precedent can judge their future career.

Currently, they have to risk that their materials and results are stored
securely and keept in private from any any unathorized actor (both
curious employee, and malicious attacker).

Our protocol allows taking such tests anonymously, and therefore getting
rid of the strong trust assumption put on the laboratories and their IT
systems.

@@

\subsection{Contribution}
We contribute to the field of fair-exchanges by proposing a simple,
practical, and strongly anonymous framework that does not rely on
centralized trusted-third party, but on decentralized blockchain and
distributed content addressable networking.

@@

\begin{itemize}
\item Anonimity:
throughout the whole transaction the customer stays anonymous to all external observers.
\item Fairness:
at each step of the protocol, both parties are incentivised to act accordingly to the protocol; otherwise the misbehaving party ends up in worst position.
\item Dispute resolution: at each step of the protocol the customer can open a dispute win the case iff the SP misbehaved.
\item TTP-less: our protocol does not rely on trusted-third party to conduct transactions in fairly manner. Only in case of dispute the centralized justice is invlolved (the justice decentralisation is discussed in section ~\ref{future-work}.
\item Physical materials: our protocol allows providing not only
  digital but also physical materials to the service provider.
\end{itemize}

@@

\begin{itemize}
    \item the TTP does not misbehave or collude with any party. 
    \item The customer's and merchant's banks enable confidental transactions and both share commit-buffer where the value is locked until the transaction is finished.   
    \item All banks mantain a global list of coin's serial numbers to prevent double-spending problem. 
    \item The source cabinet and delivery cabinet exists, and in both the product access is protected by password.
    \item Delivery cabinet is equppted with a video camera that records the moment when the customer opens the package, and provide a way to submit the video to TTP in case of a dispute. 
    \item Delivery agent exist and is trusted. 
    \item Communication channels between parties provides anonymity.
\end{itemize}

@@

Themis~\cite{meng2019themis} is a fair-exchange
protocol, which uses blockchain instead of TTP. It provide escrow
services for secure exchanging between cryptocurrencies and digital
goods.

Authors highlight that a widely-used atomic exchange mechanism HTLC
(Hashed Time-lock Contract) is vulnerable to denial of service (DoS)
attacks. While Multi-Signature Schemes depends on the Trusted Third
Party (TTP) making them vulnerable to collusion attacks. Such TTP can
collude with one party and take the locked funds. It can also refuse
settling disputes and lock the hosted funds.

Themis is a decentralized system that provides an escrow and dispute
resolution. It claims to satisfy following requirements:

\begin{itemize}
    \item Fairness: Either both seller and buyer obtain all the goods, or they both obtain nothing.
    \item Security: The funds are locked until the transaction is completed.
    \item Passivity: If no dispute arise, the third-party does not need to involve in the transaction.
    \item Correctness: Transactions and disputes are executed according to a priori agreed protocol rules.
    \item Dependability: There is no single point of failure vulnerable to DoS attack.
    \item Privacy: If the dispute does not arise, the third-party does not know if the transaction completes. If the dispute arises, only the related parties are aware of it.    
\end{itemize}

@@

Then, both Alice and Bob, takes their keys, and split them into
\(n=2t+1\) secret shares using Shamir Secret Shamir protocol, where
\(n\) is the number of mediators that participate in the decentralized
network, and \(t+1\) becomes the threshold of sufficient number of
mediators that can reconstruct the secret key.

Next, both Alice and Bob, take their key shares, and encrypt each
\(i\)-th key share using public key of \(i\)-th mediator. As a result
Alice's secret \(x_A\) becomes \({c^A_1, c^A_2,...,c^A_n}\), and Bob's
secret \(x_B\) becomes \({c^B_1, c^B_2,...,c^B_n}\), where
\(c_i = E_{M_i}(P_i)\) is the encrypted \(i\)-th key share using
\(i\)-th mediator public key \(M_i\).

@@

In case of dispute, the decentralized network of mediators settle the
conflict and grand one winning party, the other party secret key,
letting him to withdraw the funds.

The honesty of mediators is achieved by the monetary incentivization and
reputation system.

@@

However, the system doesn't achieve full anonimity but pseudonimity (see
section \ref{pseudo-anon}). Also the protocol does not
cover the case of dispute between the customer and the SP.

@@

Themis~\cite{meng2019themis} besides providing fair-exchange protocol,
also offers a semi-autonomous decentralised dispute resolution system,
which comply with the web3 postulates of decentralised web. Themis
resolve disputes by set of voluntary anonymous mediators participating
in a voting and deciding whether a party misbehaved. The honesty of
mediators is achieved by the monetary incentivization and reputation
system.

@@

Bitcoin introduced a way of decentralizing not only the currency system,
but also other similary working centralized trusted third parties
including the message board.

@@

\subsection{Pseudo-anonymous vs anonymous blockchain}
Privacy is a concept used in almost all kinds of social sciences like
philosophy, psychology, sociology, and legal. The multidisciplinary
nature leads to ambigous definitions~\cite{smith2011information}. For
the purpose of our work we rely on more concrete definitions,
i.e.~confidentality and anonimity.

@@

The cryptocurrencies that natively support anonymous transactions are
Monero~\cite{van2013cryptonote} (via Bulletproofs~\cite{Bulletpr14, bunz2018bulletproofs}) and ZCash~\cite{sasson2014zerocash} (via zk-SNARK~\cite{ben2013snarks}), Grin~\cite{fuchsbauer2019aggregate} (via Mimblewimble~\cite{httpsdow19}).

There are also techniques that can be deployed on non-anonymous
blockchains, the so called mixers: Ethereum's Tornado
Cash\cite{pertsev2019tornado}, Bitcoin's Wasabi\cite{WasabiWa56} (uses
CoinJoin \cite{CoinJoin41}) that literaly gather together users into an
\textit{anonymity set}, which then collude together in order to launder the
transactions, in such a way that to a observer the likelihood of the
sender of each transaction was equiprobable for any user from the
anonymity set.

Some systems guarantee pseudonomity rather than anonymity. Pseudonomity,
allows uses to hide their real identity behind the pseudonim. Despite
the whole system is transparent and allows linking actions to one
identity, the system is considered anonymous as long as the link between
pseudonym and real identity is secret. This assumption is hard to
satisfy in practice, as the KYC (Know You Customer) and AML (Anti Money
Laundering) regulations require users to reveal their real identity on
most of the cryptocurrencies exchanges. This makes the anonymity of the
user dependent on the security of the IT system. Moreover, some
correlations can be infered merely by the analysis of transactions
\cite{androulaki2013evaluating, ober2013structure}. Most of the
blockchains, including Bitcoin and Ethereum achieve this kind of
pseudonimity.

The relations between these terms are ilustrated in the figure~\ref{fig:anonimity-confidentality}.

\begin{figure}[h!]
\caption{Scenario of path where both the customer and  the SP are behaving correctly}
\centering
\includegraphics[width=9cm]{anonimity-confidentality.png}
\label{fig:anonimity-confidentality}
\end{figure}

People who call tracable and linkable blockchains to be anonymous base
on a strong assumption that the identification is impossible, infeasable
or at least plausably unlikely. We require the system for anonymous
payments to satisfy anonymilty via untraceability or unlinkability. We
don't pay much attention to confidentiality as it doesn't bring much
value to the protocol.

@@

As the message board could be achieved by most of the blockchanis, the
anonymous payments isn't so prevalent, and provable storage network is a
functionality of a few specialized blockchains.

@@

\subsubsection{Step 1: Package delivery}\label{step-1-package-delivery}

They protocol start once the customer delivers package \(\mathrm{pkg}\)
to SP.

In return, the SP issue an Proof-of-Delivery (POD) confirmation. The
confirmation encompasses timestamp, invoice (see section \ref{payment-for-services}), and signature.

@@

\subsubsection{Step 2: Payment}\label{step-2-payment}

Having POD, SP can not reject receiving the package. At this point the
customer should pay for the invoice according to selected cryptocurrency
system (see section~\ref{payment-for-services}).

In return, the customer receives the attestation that should be used in
case of a dispute.

@@

\subsubsection{Step 3: Provision of
service}\label{step-3-provision-of-service}

@@

\subsubsection{Step 4: Results
publication}\label{step-4-results-publication}

@@

\subsubsection{Step 5: Proof of provision
publication}\label{step-5-proof-of-provision-publication}

@@

\subsubsection{Step 6: Proof-of-provision
notification}\label{step-6-proof-of-provision-notification}

@@

\subsubsection{Step 7: Results download}\label{step-7-results-download}

@@

\subsubsection{Model}\label{model}

@@

\begin{align*} 
  \forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} \mathrm{can\ move\ the\ protocol\ \\
  to\ the\ non\-disadvantaged\ position} 
\end{align*}

\paragraph{Assumptions}\label{assumptions}

@@

\item
  Both parties start from neutral position (•).
\item
  Both parties, by completing a transaction, end up in advantaged
  positions (+). In other words, they have intrinsic motivation to
  initialise the transaction.
\item
  We assume the steps of the protocol to be atomic, there are no
  intermediate steps.
\item
  Repeating the first step starts new transaction. Repeating any other
  step is considered abnormal and gets ignored. For example paying for
  the invoice twice does not cause any effect on the curse of protocol.
\item
  Once published, the results are available to the customer in the
  content storage. The idea of guaranteeing it cryptographically is
  discussed in section ~\ref{future-work}.
\item
  The protocol can go only forward, there is no way of revert any
  action.
\item
  Losing the dispute leads to punishment that is greater than any
  reward, which leads to disadvantaged position. Hence, the rational
  customer won't start a dispute that he is not sure to win.
\item
  Winning the dispute leads to neutral position (•)
\item
  Both the customer and the SP are rational (selfish). They always
  prefer go from worst position to better position, but also risk
  temporary worst position in favour for later better position iff it's
  assured that they won't stuck in worst position.
\end{itemize}

\subsubsection{Steps}\label{steps}

@@

The possible directions for mitigation of such issue are to either (1)
replace Justice with decentralised autonomous organisations (DAO) like
proposed in Themis~\cite{meng2019themis} or
Kleros~\cite{lesaege2018kleros}; or (2) make it infeasible to provide
incorrect results.

>>>>

\tfootnote{This paragraph of the first footnote will contain support 
information, including sponsor and financial support acknowledgement. For 
example, ``This work was supported in part by the U.S. Department of 
Commerce under Grant BS123456.''}

@@

\begin{abstract}
Service providers like lawyers, laboratories, auditors, or banks, to
provide services, require customers to submit data often
associated with their personal information. This situation exposes
customers to privacy risks. However, most service providers use personal information merely for logistic operations like payments
and communication and could provide services anonymously if other means of logistics exist.

We propose a framework for coordinating local anonymous service
provision. Our proposal uses blockchain for both anonymous payments and proofs of existence (so-called message board) and content-addressable network (e.g.~IPFS) for results delivery.

A local service provider can employ our framework to provide
services without collecting any personal information. Possible
applications for this framework include anonymous clinical drug testing,
steroid testing, parenting testing, anonymous legal advice, or
anonymous financial trustworthiness evaluation.

In case of dispute, either due to exceeding deadlines or providing
incorrect results, the customer can disclose the whole interaction and
prove to justice (police or court) the misbehaviour of the service
provider.

We analyse the protocol in the context of fairness and discuss further
extensions to an anonymous delivery system, payment with cash, and
decentralised conflict resolution system.

Our framework can enable various services currently based on unacceptable trust assumptions to the SP.
\end{abstract}

\begin{keywords}
Blockchain, anonymity, fair-exchange, physical delivery
\end{keywords}

@@

\maketitle
\section{Introduction}
Service providers (SP) like lawyers, laboratories, auditors, or banks,
to provide services, require data that is often associated with the user
identity.

Providing personal information exposes users to privacy risks,
i.e. potential loss of control over personal
information~\cite{smith2011information}.

Such user information can be used deliberately or unintentionally
(e.g., by theft) for insider disclosure, unauthorised access, or
commercial gains. For example, by reselling it to marketers, financial
institutions, other businesses, government agencies, or even
cybercriminals. Which in turn can lead to profiled advertisements or
criminal activities like identity theft or illegal tracking and
surveillance~\cite{smith2011information}.

Important individuals like top government, influencers, or celebrities are especially vulnerable to this kind of attack as exposure of their
health records, purchase habits, or legal documents can threaten their
reputation, position, or can be used for blackmailing.

The guarantee of the privacy of the data is often based merely on a
trust assumptions and security of IT system. However, most of the SP
do not need the personal information for any other reason than payment
or communication, which should be considered secondary compared to
actual service provision.

It would be desirable for the user to keep its identity private while the service provider still provides its services. This could lead to reduced
trust that users have to put on SP and less responsibility borne by SP.

@@

Patients willing to take a steroid test, drug tests, venereal diseases
test, paternity test — have strong incentive to keep the whole
procedure private. Merely the fact that they took the test — without
exposing the results — is suggestive enough to act as a premise in
case of a conflict.

Especially celebrities, politicians and public persona are prone to this kind of problem as such precedent can negatively influence their future career.

Currently, they have to risk that their materials and results are stored
securely and kept in private from any unauthorised actor (both
curious employee, and malicious attacker).

Our protocol allows taking such tests anonymously and therefore getting
rid of the strong trust assumption put on the laboratories and their IT
systems.

@@

\subsection{Contribution}
We contribute to the field of fair-exchanges by proposing a simple,
practical, and strongly anonymous framework that does not rely on
centralised trusted-third party, but on decentralised blockchain and
distributed content addressable networking.

@@

\begin{itemize}
\item Anonimity:
throughout the whole transaction the customer stays anonymous to all external observers.
\item Fairness:
at each step of the protocol, both parties are incentivised to act accordingly to the protocol; otherwise the misbehaving party ends up in worst position.
\item Dispute resolution: at each step of the protocol the customer can open a dispute win the case iff the SP misbehaved.
\item TTP-less: our protocol does not rely on trusted-third party to conduct transactions in fairly manner. Only in case of dispute the centralised justice is invlolved (the justice decentralisation is discussed in section ~\ref{future-work}.
\item Physical materials: our protocol allows providing not only
  digital but also physical materials to the service provider.
\end{itemize}

@@

\begin{itemize}
    \item the TTP does not misbehave or collude with any party. 
    \item The customer's and merchant's banks enable confidental transactions and both share commit-buffer where the value is locked until the transaction is finished.   
    \item All banks mantain a global list of coin's serial numbers to prevent double-spending problem. 
    \item The source cabinet and delivery cabinet exists, and in both the product access is protected by password.
    \item Delivery cabinet is equipped with a video camera that records the moment when the customer opens the package, and provide a way to submit the video to TTP in case of a dispute. 
    \item There exists a trusted delivery agent.
    \item Communication channels between parties provides anonymity.
\end{itemize}

@@

Themis~\cite{meng2019themis} is a fair-exchange
protocol, which uses blockchain instead of TTP. It provide escrow
services for secure exchanging between cryptocurrencies and digital goods, and decentralised dispute resolution system for resolving conflicts.

@@

Then, both Alice and Bob, takes their keys, and split them into
\(n=2t+1\) secret shares using Shamir Secret Shamir protocol, where
\(n\) is the number of mediators that participate in the decentralised
network, and \(t+1\) becomes the threshold of sufficient number of
mediators that can reconstruct the secret key.

Next, both Alice and Bob, take their key shares, and encrypt each
\textit{i}-th key share using public key of \textit{i}-th mediator. As a result
Alice's secret \(x_A\) becomes \({c^A_1, c^A_2,...,c^A_n}\), and Bob's
secret \(x_B\) becomes \({c^B_1, c^B_2,...,c^B_n}\), where
\(c_i = E_{M_i}(P_i)\) is the encrypted \(i\)-th key share using
\(i\)-th mediator public key \(M_i\).

@@

In case of dispute, the decentralised network of mediators settle the
conflict and grand one winning party, the other party secret key,
letting him to withdraw the funds.

The honesty of mediators is achieved by the monetary incentivisation and
reputation system.

@@

However, the system doesn't achieve full anonimity but pseudonimity (see
section~\ref{pseudo-anon}). Also the protocol does not
cover the case of dispute between the parties.

@@

Themis~\cite{meng2019themis} besides providing fair-exchange protocol,
also offers a semi-autonomous decentralised dispute resolution system,
which comply with the web3 postulates of decentralised web. Themis
resolve disputes by set of voluntary anonymous mediators participating
in a voting and deciding whether a party misbehaved. The honesty of
mediators is achieved by the monetary incentivisation and reputation
system.

@@

Bitcoin introduced a way of decentralising not only the currency system,
but also other similary working centralised trusted third parties
including the message board.

@@

\subsection{Pseudo-anonymous vs anonymous blockchain}

Privacy is a concept used in almost all kinds of social sciences like philosophy, psychology, sociology, and legal. The multidisciplinary nature leads to ambigous definitions~\cite{smith2011information}. For the purpose of our work we rely on more concrete definitions, i.e.~confidentality and anonimity.

@@

There are also techniques that can be deployed on non-anonymous blockchains, the so called mixers that literaly gather together users into an \textit{anonymity set}, which then collude together in order to launder the transactions, in such a way that to a observer the likelihood of the sender of each transaction was equiprobable for any user from the anonymity set.

Some systems guarantee pseudonomity rather than anonymity. Pseudonomity, allows uses to hide their real identity behind the pseudonim. Despite the whole system is transparent and allows linking actions to one identity, the system is considered anonymous as long as the link between pseudonym and real identity is secret. This assumption is hard to satisfy in practice, as the KYC (Know You Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity on most of the cryptocurrencies exchanges. This makes the anonymity of the user dependent on the security of the IT system. Moreover, some correlations can be infered merely by the analysis of transactions \cite{androulaki2013evaluating, ober2013structure}.

The relations between these terms are ilustrated in the figure~\ref{fig:anonymity-diagram}.

\begin{figure}[h!]
\caption{}
\centering
\includegraphics[width=9cm]{anonymity-diagram.png}
\label{fig:anonymity-diagram}
\end{figure}

Let us assume the Alice to be the customer willing to keep her identity private (anonymous) and Bob be the public SP. Alice controls two blockchain addresses 1 and 2, the connection between her real identity and the first address was compromised, and therefore the identification is possible, the connection between the second pseudonym is still unknown therefore anonymous. Alice takes two actions; the first one from the compromised address and the second one from anonymous one. The first action is confidential; therefore even though the psudonym has been compromised the action can not be associated with the Alice. The second action is transparent, therefore the Alice's anonymity is maintained as long as the connection to the second pseudonym is concealed.

The privacy-preserving blockchains are the ones that maintain anonymity via untraceability and unlikability, not via assumption that the connection between an address and the real identity is concealed.

Blockchains that natively support confidential transactions are
Monero~\cite{van2013cryptonote} (via Ring Signatures~\cite{cryptoeprint:2015:1098} and Bulletproofs~\cite{Bulletpr14, bunz2018bulletproofs}) and ZCash~\cite{sasson2014zerocash} (via zkSNARK~\cite{ben2013snarks}), Grin~\cite{fuchsbauer2019aggregate} (via Mimblewimble~\cite{httpsdow19}).

Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash\cite{pertsev2019tornado} (via zkSNARK~\cite{groth2016size} and MiMC~\cite{albrecht2016mimc}), Bitcoin's Wasabi\cite{WasabiWa56} (via CoinJoin \cite{CoinJoin41}).

@@

As the message board could be achieved by most of the blockchanis, the
anonymous payments isn't so prevalent, and provable storage network is a
functionality of a few specialised blockchains.

@@

\paragraph{Step 0: Preparation}\label{step-0-preparation}

The customer collects all the $\mathrm{materials}$ required by the SP, generate an encryption $\mathrm{key}$ print it on a paper as a QR code, and pack them together into a package $\mathrm{pkg}$.

\paragraph{Step 1: Package delivery}\label{step-1-package-delivery}

They protocol starts once the customer delivers package $\mathrm{pkg}$ and the SP accepts its content. In return, the SP issue a $\mathrm{PoD}$ with agreed upfront payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$ and current time $\mathrm{T}_\mathrm{issue}$. Also, the $\mathrm{PoD}$ consist of randomly generated unique number $\mathrm{nonce}$, which will allow associating all actions related to the transaction throughout the protocol. Finally, the digital signature $\mathrm{sig}_\mathrm{SP}$ on the $\mathrm{PoD}$ created with the SP's secret key guarantee non-repudiation.

We assume this step to be fully physical, that is, $\mathrm{pkg}$ consist of physical materials, $\mathrm{PoD}$ is in a form of e.g., QR code printed on paper receipt.

$\mathrm{PoD}$ could be published on a message board (similarly to $\mathrm{PoP}$); however, since the $\mathrm{pkg}$ is delivered personally or via trusted person, the confirmation can be issued in person as well. If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on message board (further extension to anonymous delivery system is discussed in section \ref{future-work}).

@@

\paragraph{Step 2: Payment}\label{step-2-payment}

Having the PoD issued, the SP can not reject receiving the package. At this point the
customer should pay for the transaction with agreed upfront cryptocurrency system (see section~\ref{payment-for-services}).

In return, the customer receives the $\mathrm{attestation}$ that should be disclosed in case of a dispute.

@@

\paragraph{Step 3: Provision of
service}\label{step-3-provision-of-service}

@@

\paragraph{Step 4: Results
publication}\label{step-4-results-publication}

@@

\paragraph{Step 5: Proof of provision
publication}\label{step-5-proof-of-provision-publication}

@@

\paragraph{Step 6: Proof-of-provision
notification}\label{step-6-proof-of-provision-notification}

@@

\paragraph{Step 7: Results download}\label{step-7-results-download}

@@

\subsection{Model}\label{model}

@@

\begin{align*} 
  \forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} \mathrm{can\ move\ the\ protocol\ \\
  to\ the\ non\ disadvantaged\ position} 
\end{align*}

\subsection{Assumptions}\label{assumptions}

@@

\item
  Both parties start from neutral position (•).
\item
  Both parties, by completing a transaction, end up in advantaged
  positions (+). In other words, they have intrinsic motivation to
  initialise the transaction.
\item
  We assume the steps of the protocol to be atomic, there are no
  intermediate steps.
\item
  Repeating the first step starts new transaction. Repeating any other
  step is considered abnormal and gets ignored. For example paying for
  the invoice twice does not cause any effect on the curse of protocol.
\item
  Once published, the results are available to the customer in the
  content storage. The idea of guaranteeing it cryptographically is
  discussed in section ~\ref{future-work}.
\item
  The protocol can go only forward, there is no way of revert any
  action.
\item
  Losing the dispute leads to punishment that is greater than any
  reward, which leads to disadvantaged position (-). Hence, the rational
  customer won't start a dispute that he is not sure to win.
\item
  Winning the dispute leads to neutral position (•).
\item
  Both the customer and the SP are rational (selfish). They always
  prefer go from worst position to better position, but also risk
  temporary worst position in favour for later better position iff it's
  assured that they won't stuck in worst position.
\end{itemize}

\subsection{Steps}\label{steps}

@@

The possible directions for mitigation of such issue are to either (1)
replace justice with decentralised autonomous organisations (DAO) like
proposed in Themis~\cite{meng2019themis} or
Kleros~\cite{lesaege2018kleros}; or (2) make it infeasible to provide
incorrect results.
